### 2018-11-28 chapters/2-methods.tex
mention feature normalization

For image types ADCₘ, ADCₖ, K a corresponding data set of 100 data points and
1281 features were used to build models for predicting prostate lesion
aggressiveness based on Gleason score, while in image types T₂w and T₂ the
number of features was 1631. The data points were divided into two groups by
Gleason score, low and high (3+3 and >3+3, respectively). Logistic regression
with either L1 or L2 regularization \citep{Friedman2010} implemented by Python
Scikit-learn library \citep{Pedregosa2011} were used to train the low vs high
Gleason score classifiers. Both regularization mechanisms compensate the high
dimensionality of the data by penalizing large coefficient values of the
inferred linear models, which in turn makes them less likely to overfit to the
training data and more able to generalize to data unseen in the training phase.

>>>>

For image types ADCₘ, ADCₖ, K a corresponding data set of 100 data points and
1281 features were used to build models for predicting prostate lesion
aggressiveness based on Gleason score, while in image types T₂w and T₂ the
number of features was 1631. The features were normalized to zero mean and unit
variance. The data points were divided into two groups by Gleason score, low
and high (3+3 and >3+3, respectively). Logistic regression with either L1 or L2
regularization \citep{Friedman2010} implemented by Python Scikit-learn library
\citep{Pedregosa2011} were used to train the low vs high Gleason score
classifiers. Both regularization mechanisms compensate the high dimensionality
of the data by penalizing large coefficient values of the inferred linear
models, which in turn makes them less likely to overfit to the training data
and more able to generalize to data unseen in the training phase.

### 2018-11-28 chapters/3-results.tex
mention feature normalization

When using all features and L1 regularization (Table~\ref{tab:auc_imagetype}),
T₂w had AUC=0.82, DWI derived parametric maps (ADCₘ, ADCₖ, K) had AUC between
0.64 to 0.71, and T₂ derived features had AUC=0.58.

In contrast to L1, L2 regularization yielded better performance for all image
types except T₂w where AUC dropped to 0.68. DWI derived parametric maps (ADCₘ,
ADCₖ, K) had AUC between 0.69 to 0.73, and T₂ derived features had AUC=0.70.

>>>>

When using all features and L1 regularization (Table~\ref{tab:auc_imagetype}),
T₂w had AUC=0.82, DWI derived parametric maps (ADCₘ, ADCₖ, K) had AUC range
0.64--0.71, and T₂ derived features had AUC=0.58.

In contrast to L1, L2 regularization yielded better performance for all image
types except T₂w where AUC dropped to 0.68. DWI derived parametric maps (ADCₘ,
ADCₖ, K) had AUC range 0.69--0.73, and T₂ derived features had AUC=0.70.
